### 2024-09-17 actuarial.qmd
20240916 - compelling

In general, many so-called experts are "pseudo-experts" who do not know the boundaries of their competence—that is, they do not know what they do not know; they have the illusion of validity of their predictions and are [overconfident](#sec-cognitiveBiasesOverconfidence) about their predictions [@Kahneman2011].
Yet, many people arrogantly proclaim to have predictive powers, including in low-validity environments such as fantasy football.
Indeed, pundits are more likely to be television guests if they are opinionated, clear, and (overly) confident and make big, bold predictions, because they are more entertaining [even though they tend to be less accurate than individuals whose thinking is more complex and less decisive; @Kahneman2011; @Silver2012].
Consider sports pundits like Stephen A. Smith and Skip Bayless who make bold predictions with uber confidence.
[Optimism](#sec-cognitiveBiasesOptimism) and [(over)confidence](#sec-cognitiveBiasesOverconfidence) are valued by society [@Kahneman2011].
Nevertheless, true experts know their limits in terms of knowledge and ability to predict.

>>>>

In general, many so-called experts are "pseudo-experts" who do not know the boundaries of their competence—that is, they do not know what they do not know; they have the illusion of validity of their predictions and are [overconfident](#sec-cognitiveBiasesOverconfidence) about their predictions [@Kahneman2011].
Yet, many people arrogantly proclaim to have predictive powers, including in low-validity environments such as fantasy football.
Indeed, pundits are more likely to be television guests if they are opinionated, clear, and (overly) confident and make big, bold predictions, because they are more entertaining and their predictions seem more compelling [even though they tend to be less accurate than individuals whose thinking is more complex and less decisive; @Kahneman2011; @Silver2012].
Consider sports pundits like Stephen A. Smith and Skip Bayless who make bold predictions with uber confidence.
[Optimism](#sec-cognitiveBiasesOptimism) and [(over)confidence](#sec-cognitiveBiasesOverconfidence) are valued by society [@Kahneman2011].
Nevertheless, true experts know their limits in terms of knowledge and ability to predict.
